Analysis plan

### 2023-03-15 02. Design/MSG-P2312-Analysis Plan-1-clusters.rmd
Update MSG-P2312-Analysis Plan-1-clusters.rmd
Re-arranged Mike's notes, added notes from lab, updated deduplication process

<!-- # MIKES COMMENTS -->

<!-- Proofread for typos -->

@@

Both data sources will be checked for duplication and deduplicated. The
daily check-in data has no true unique identifier. The roster data is
uniquely identified by `employee_e_mail_address` and `snapshot_date`.
The roster data *should not* have any duplications on
`employee_e_mail_address` and `snapshot_date`, but this will be checked.
To create a unique identifier in the daily check-in data, we will
following process:

1.  Start with check-in data from one month (call this *month 1*)

2.  Transform supervisor name to match format of the roster data

3.  Join roster data from the previous month (call this *month 0*) on
    employee name, staff or service office, department ID and supervisor
    name

4.  Check to see if any rows are missing `employee_e_mail_address` after
    the join

5.  For any rows missing `employee_e_mail_address`, join roster data
    from data from *month 1*

6.  Check to see if any rows are missing `employee_e_mail_address` after
    the join

7.  For any rows missing `employee_e_mail_address`, join roster data
    from data from *month 2*

@@

After this, the combined data *should* be uniquely identified by
`employee_e_mail_address` and `date`. The data set will contain all the
daily check-in and roster information across the observation window.

@@

@@

>>>>

#Proofread for typos

@@

Both data sources will be checked for duplication and deduplicated. The
daily check-in data has no true unique identifier. The roster data is
uniquely identified by `employee_e_mail_address` and `snapshot_date`, but some entries for `employee_e_mail_address` are null. 
The roster data *should not* have any duplications on
`employee_e_mail_address` and `snapshot_date`, but this will be checked.
To create a unique identifier in the daily check-in data, we will
following process:

1.  Import all months of check-in data

2.  Transform supervisor name to match format of the roster data, and create new variables for the end of the month prior to the check-in date and the end of the month of the check-in date to match the `snapshot_date`

3.  Inner join check-in and roster data  on employee name, department ID and supervisor name, and prior month, creating a new data set called `joined data 1`

4.  Remove rows in `joined data 1` from the check-in data (i.e. anti-join), then inner join check-in and roster data  on employee name, department ID and supervisor name, and current month, creating a new data set called `joined data 2`

5.  Bind row from `joined data 1` and `joined data 2`, creating a new data set called `bound data`

6.  Select the distinct employee email addresses and names from `bound data` and assign a unique identifier to this called `person_id`, creating a new data set called `unique ID`

7.  Join the `unique ID` to `bound data` on employee email addresses and names

@@

After this, the combined data *should* be uniquely identified by
`person_id` and `date`. The data set will contain all the
daily check-in and roster information across the observation window.

@@

ADD TEAM CLAFFICATION RULES FOR STAFF AND TEAM ANALYSIS

@@

<!-- MD: There are policy definitions of remote. 100% of days could be classified as all remote (separate rule); policy rules if you are not a full-time worker (you are a teleworker) you report two days a pay period; could align cut-offs with policy type definitions. # of days cutoff.  -->
<!-- Ben: the way I defined groups is mutually exclusive, but does not need to be that way -->
<!-- Ben: Other rules to examine -->
<!-- JB: policy side, missingness (whole groups of people missing on some dimension tells you something about data collection procedure) -->

<!-- MD: other roster data might be relevant - position category could give diff patterns for people who are analysts vs. building inspectors or supervisors vs. non supervisors, pay grade; lower pay grade less likely to have remote option -->
<!-- Ben: confusion matrix - assume that some group works in this sort of way but guess what they don’t! What is happening? -->

<!-- MD: categories: onsite flexible, onsite, remote; but not sure of levels of going in within categories. What is the average of going in? -->
<!-- MD: discretion of work patterns by regional commissioners  -->
